Predicting information integration in pragmatic word learning across development

### 2021-01-05 papers/full_paper/Supplementary_information.Rmd
add new supp material

## No common ground model

@@

ex_3_cor_plot <- ex_3_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  left_join(., ex_3_pred %>%
    ungroup()%>%
    filter(model == "data") %>%
    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
    select(-model)
  )%>%
  mutate(model =  case_when(model == "integration_noise" ~ "Integration",
                            model == "no_informativeness_noise" ~ "No informativeness",
                            model == "no_common_ground_noise" ~ "No common ground"
                            ))

@@

```{r ex3noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.align = "center", out.width="80%", fig.height=3}
ex3_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No common ground")
  )

ggplot(ex3_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

ex_4_cor_plot <- ex_4_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  left_join(., ex_4_pred %>%
    ungroup()%>%
    filter(model == "data") %>%
    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
    select(-model)
  )%>%
  mutate(model =  case_when(model == "integration_noise" ~ "Integration",
                            model == "no_informativeness" ~ "No informativeness",
                            model == "no_common_ground" ~ "No common ground"
                            ))

@@

ex4_bf <- bind_rows(
  ex4_pragm_model_noise_loglike,
  ex4_flat_prior_model_noise_loglike,
  ex4_prior_only_model_noise_loglike
) %>% spread(model, logP) %>%
  mutate("Integration > No informativeness" = exp(integration_noise - no_informativeness),
         "Integration > No common ground" = exp(integration_noise - no_common_ground),
         "No common ground > No informativeness" = exp(no_common_ground - no_informativeness)) %>%
  select(-integration_noise, -no_common_ground, -no_informativeness)%>%
  gather(Comparison, BF)%>%
  mutate(BF = formatC(BF,2))

@@

```{r ex4noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.align = "center", out.width="80%", fig.height=3}
ex4_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No common ground")
  )

ggplot(ex4_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

```{r child_bf, results = "asis", out.width="100%"}
child_ex3_bf <- child_ex3_model_comparison%>%
  select(-ci_lower, -ci_upper)%>%
  rename(Parameter = parameter)%>%
  group_by(Parameter)%>%
  spread(model, logP) %>%
  mutate("Int > No CG" = formatC(exp(pragmatic - flat_prior),2),
         "Int > No Inf" = formatC(exp(pragmatic - prior_only),2),
         "No CG > No Inf" = formatC(exp(flat_prior - prior_only),2)) %>%
  select(-pragmatic,-flat_prior, -prior_only)

apa_table(
  child_ex3_bf
  , caption = "Model comparisons in Experiment 7"
  , note = "BF = Bayes Factor, Int = Integration, No CG = No common ground, No Inf = No informativeness "
  , escape = T
)
```

```{r}
child_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No common ground")
  )
child_noise_plot <- ggplot(child_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

```{r, include = T}
child_ex3_pragm_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))
child_ex3_prior_only_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))
child_ex3_flat_prior_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))
developmental_noise_parameter <- data_frame(
  age = rep(seq(0,2, by = 0.05),3),
  Model = c(rep("Integration",41),
            rep("No common ground",41),
            rep("No informativeness",41)),
  int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41),
          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41),
          rep(child_ex3_prior_only_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41)
          ),
  slope = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41),
          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41),
          rep(child_ex3_prior_only_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41))
) %>%
  mutate(y = plogis(int + slope *age),
         age = age +3)

child_dev_noise_plot <- ggplot(developmental_noise_parameter, aes(x = age, y= y, col = Model))+
  geom_line(size = 1)+
  ylab("Noise parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

#   mutate(model = "No common ground",

@@

p_child_cor<- readRDS("../../stats/saves/child_all_models_cor.rds") %>%
  na.omit()%>%
  ungroup()%>%
  mutate(model = recode(model,
                          "Pragmatic" = "Integration",
                          "Flat prior" = "No common ground",
                          "Prior only" = "No informativeness"),
         data_mean = rep(p_child_ex3_data_binned%>%pull(mean),9),
         data_ci_upper = rep(p_child_ex3_data_binned%>%pull(ci_upper),9),
         data_ci_lower = rep(p_child_ex3_data_binned%>%pull(ci_lower),9))

>>>>

## No conversational prior model

@@

ex_3_cor_plot <- ex_3_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  left_join(., ex_3_pred %>%
    ungroup()%>%
    filter(model == "data") %>%
    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
    select(-model)
  )%>%
  mutate(model =  case_when(model == "integration_noise" ~ "Integration",
                            model == "no_informativeness_noise" ~ "No informativeness",
                            model == "no_common_ground_noise" ~ "No conversational prior"
                            ))

@@

```{r ex3noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.align = "center", out.width="80%", fig.height=3}
ex3_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No conversational prior")
  )

ggplot(ex3_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

ex_4_cor_plot <- ex_4_pred %>%
  ungroup()%>%
  filter(model != "data") %>%
  left_join(., ex_4_pred %>%
    ungroup()%>%
    filter(model == "data") %>%
    rename(data_mean = mean, data_ci_lower = ci_lower, data_ci_upper = ci_upper) %>%
    select(-model)
  )%>%
  mutate(model =  case_when(model == "integration_noise" ~ "Integration",
                            model == "no_informativeness" ~ "No informativeness",
                            model == "no_common_ground" ~ "No conversational prior"
                            ))

@@

ex4_bf <- bind_rows(
  ex4_pragm_model_noise_loglike,
  ex4_flat_prior_model_noise_loglike,
  ex4_prior_only_model_noise_loglike
) %>% spread(model, logP) %>%
  mutate("Integration > No informativeness" = exp(integration_noise - no_informativeness),
         "Integration > No conversational prior" = exp(integration_noise - no_common_ground),
         "No conversational prior > No informativeness" = exp(no_common_ground - no_informativeness)) %>%
  select(-integration_noise, -no_common_ground, -no_informativeness)%>%
  gather(Comparison, BF)%>%
  mutate(BF = formatC(BF,2))

@@

```{r ex4noise, include = T, fig.cap = "Posterior distribution of noise parameter for each model in Experiment 4", fig.align = "center", out.width="80%", fig.height=3}
ex4_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/ex4_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/ex4_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/ex4_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No conversational prior")
  )

ggplot(ex4_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

```{r child_bf, results = "asis", out.width="100%"}
child_ex3_bf <- child_ex3_model_comparison%>%
  select(-ci_lower, -ci_upper)%>%
  rename(Parameter = parameter)%>%
  group_by(Parameter)%>%
  spread(model, logP) %>%
  mutate("Int > No CP" = formatC(exp(pragmatic - flat_prior),2),
         "Int > No Inf" = formatC(exp(pragmatic - prior_only),2),
         "No CP > No Inf" = formatC(exp(flat_prior - prior_only),2)) %>%
  select(-pragmatic,-flat_prior, -prior_only)

apa_table(
  child_ex3_bf
  , caption = "Model comparisons in Experiment 7"
  , note = "BF = Bayes Factor, Int = Integration, No CP = No conversational prior, No Inf = No informativeness "
  , escape = T
)
```

```{r}
child_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No conversational prior")
  )
child_noise_plot <- ggplot(child_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

```{r, include = T}
child_ex3_pragm_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_pragm_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))
child_ex3_prior_only_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))
child_ex3_flat_prior_model_developmental_noise_param <- readRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise.rds") %>%
  filter(Parameter %in% c("noise_int","noise_slope"))  %>%
  group_by(Parameter)%>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value),
            ci_upper = hdi_upper(value))
developmental_noise_parameter <- data_frame(
  age = rep(seq(0,2, by = 0.05),3),
  Model = c(rep("Integration",41),
            rep("No conversational prior",41),
            rep("No informativeness",41)),
  int = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41),
          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41),
          rep(child_ex3_prior_only_model_developmental_noise_param%>%
                filter(Parameter == "noise_int")%>%
                pull(mean),41)
          ),
  slope = c(rep(child_ex3_pragm_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41),
          rep(child_ex3_flat_prior_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41),
          rep(child_ex3_prior_only_model_developmental_noise_param%>%
                filter(Parameter == "noise_slope")%>%
                pull(mean),41))
) %>%
  mutate(y = plogis(int + slope *age),
         age = age +3)

child_dev_noise_plot <- ggplot(developmental_noise_parameter, aes(x = age, y= y, col = Model))+
  geom_line(size = 1)+
  ylab("Noise parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_color_manual(breaks=c("Integration","No informativeness","No conversational prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

#   mutate(model = "No conversational prior",

@@

p_child_cor<- readRDS("../../stats/saves/child_all_models_cor.rds") %>%
  na.omit()%>%
  ungroup()%>%
  mutate(model = recode(model,
                          "Pragmatic" = "Integration",
                          "Flat prior" = "No conversational prior",
                          "Prior only" = "No informativeness"),
         data_mean = rep(p_child_ex3_data_binned%>%pull(mean),9),
         data_ci_upper = rep(p_child_ex3_data_binned%>%pull(ci_upper),9),
         data_ci_lower = rep(p_child_ex3_data_binned%>%pull(ci_lower),9))
